Measuring neutron star tidal deformability with Advanced LIGO: a Bayesian analysis of neutron star - black hole binary observations

### 2017-01-03 Paper/journal_submission/paper.tex
adding more figs to text

>>>>

\includegraphics[width=1.025\columnwidth,trim=1cm 0 0 0]{LambdaMedianCIWidths90pc_vs_N_AllPopulation_SNRSorted}
\includegraphics[width=1.025\columnwidth,trim=0 0 1cm 0]{LambdaCIWidths90pc_vs_N_AstroPopulation_SNRSorted}
\caption{This figure is similar to Fig.~\ref{fig:TT_LambdaError_vs_N_L500_2000_CI90_0_AllInOne},
with the difference
that events in each population have been sorted according to their
signal strength (SNR). We note that most of the information about
the NS tidal deformation comes from the loudest $5-10$ events, for
both paradigms.
\label{fig:TT_LambdaError_vs_N_L500_2000_CI90_0_AllInOne_SNRSorted}
